\begin{thebibliography}{99}

\bibitem{PIP2016}
A. H\'ebert, Applied Reactor Physics, Second Edition, Presses Internationales Polytechnique, ISBN 978-2-553-01698-1, 396 p., Montr\'eal, 2016.

\bibitem{v4}
A. H\'ebert, "Development Procedures for Version4 of
Reactor Physics Codes," Report IGE-287,
\'Ecole Polytechnique de Montr\'eal,
 Institut de G\'enie Nucl\'eaire (2006).

\bibitem{gan1}
A. H\'ebert and R.~Roy, "The GAN Generalized Driver," 
\'Ecole Polytechnique de Montr\'eal,
 Institut de G\'enie Nucl\'eaire (2000).

\bibitem{ganlib5}
A. H\'ebert and R.~Roy,
``The Ganlib5 kernel guide (64--bit clean version),"
Report IGE-332, \'Ecole Polytechnique de Montr\'eal, January 2013.

\bibitem{dragon}
G. Marleau, A. H\'ebert and R. Roy,
"A User Guide for DRAGON Version5,"
Report IGE-335, \'Ecole Polytechnique de Montr\'eal,
Institut de G\'enie Nucl\'eaire (2014).

\bibitem{trivac}
A. H\'ebert, "A User Guide for TRIVAC Version4,"
Report IGE-293, \'Ecole Polytechnique de Montr\'eal,
Institut de G\'enie Nucl\'eaire (2007).

\bibitem{ah1}
A. H\'ebert, "TRIVAC, A Modular Diffusion Code for Fuel Management and 
Design Applications," {\sl Nucl. J. of Canada}, Vol. 1, No. 4, 325 (1987).

\bibitem{ah2}
A. H\'ebert, "Application of the Hermite Method for Finite Element 
Reactor Calculations," {\sl Nucl. Sci. Eng.}, {\bf 91}, 34 (1985).

\bibitem{ah3}
A. H\'ebert, "Variational Principles and Convergence Acceleration 
Strategies for the Neutron Diffusion Equation," {\sl Nucl. Sci. Eng.}, 
{\bf 91}, 414 (1985).

\bibitem{ah4}
A. H\'ebert, "Preconditioning the Power Method for Reactor Calculations,"
{\sl Nucl. Sci. Eng.}, {\bf 94}, 1 (1986).

\bibitem{ah5}
A. H\'ebert, "Development of the Nodal Collocation Method for Solving 
the Neutron Diffusion Equation," {\sl Ann. Nucl. Energy}, {\bf 14}, 
527 (1987).

\bibitem{ah6}
A. H\'ebert, "Application of a Dual Variational Formulation to Finite 
Element Reactor Calculations," {\sl Ann. nucl. Energy}, {\bf 20}, 823 (1993).

\bibitem{donjon}
E. Varin,  A. H\'ebert, J. Koclas and R. Roy, "A User Guide for DONJON,"
Report IGE-208, , \'Ecole Polytechnique de Montr\'eal,
Institut de G\'enie Nucl\'eaire (2005).

\bibitem{donjstruc}
E. Varin, A. H\'ebert,
"Data Structures for DONJON," 
Report IGE-226, \'Ecole Polytechnique de Montr\'eal,
 Institut de G\'enie Nucl\'eaire (2003).

\bibitem{rozon}
D. Rozon, 
"Gestion du combustible nucl\'eaire. Notes de cours Ene6109,"
Report IGE-298, \'Ecole Polytechnique de Montr\'eal,
 Institut de G\'enie Nucl\'eaire (2007).

\bibitem{chambon}
R. Chambon,
{\sl Optimisation de la gestion du combustible dans les r\'eacteurs
CANDU refroidis \`a l'eau l\'eg\`ere}, Ph. D. Thesis, \'Ecole Polytechnique de Montr\'eal (2006). 

\bibitem{Intech2011}
A. H\'ebert, {\sl Revisiting the Ceschino Interpolation Method}, in {\sl MATLAB -- A Ubiquitous Tool for the Practical
Engineer}, Clara M. Ionescu (Ed.), InTech Open Access Publisher, ISBN 978-953-307-907-3, Croatia, 2011.

\bibitem{dragstruc}
A. H\'ebert, G. Marleau and R. Roy, 
"A description of the DRAGON Data Structures," 
Report IGE-295, \'Ecole Polytechnique de Montr\'eal,
 Institut de G\'enie Nucl\'eaire (2007).

\bibitem{hst}
E. Varin and G. Marleau, ``CANDU reactor core simulations using fully coupled DRAGON and DONJON calculations,"
{\sl Ann. Nucl. Energy}, {\bf 33}, 682 (2006).

\bibitem{tajmouati}
J. Tajmouati, ``Optimisation de la gestion du combustible enrichi d'un r\'eacteur CANDU
avec prise en compte des param\`etres locaux," Ph. D. thesis, \'Ecole Polytechnique de
Montr\'eal (1993).

\bibitem{sissaoui}
M. T. Sissaoui, G. Marleau and D. Rozon, ``CANDU Reactor Simulations Using the
Feedback Model with Actinide Burnup History," {\sl Nucl. Technology}, {\bf 125},
197 (1999).

\bibitem{cle2000}
R.~Roy, ``The CLE-2000 Tool-box," 
Report IGE-163, \'Ecole Polytechnique de Montr\'eal,
 Institut de G\'enie Nucl\'eaire (1999).

\bibitem{gan2}
A. H\'ebert and R.~Roy, "A Programmer's Guide for the GAN Generalized Driver --
FORTRAN-77 version," Report IGE-158, \'Ecole Polytechnique de Montr\'eal,
Institut de G\'enie Nucl\'eaire (1994).

\bibitem{anl}
"Argonne Code Center: Benchmark Problem Book," ANL-7416, Supp. 2, ID11-A2, 
Argonne National Laboratory (1977).

\bibitem{apollo2}
S. Loubi\`ere, R. Sanchez, M. Coste, {\bf A. H\'ebert}, Z. Stankovski, C. Van Der Gucht and I. Zmijarevic, ``APOLLO2,
Twelve Years Later," paper presented at the {\sl Int. Conf. on Mathematics and Computation,
Reactor Physics and Environmental Analysis in Nuclear Applications}, Madrid, Spain, September 27--30, 1999.

\bibitem{Griffiths94}
J.~Griffiths,  
\textsl{WIMS--AECL Users Manual},
Report RC-1176, Atomic Energy of Canada Limited, Chalk River, Ontario (1994).

\bibitem{Donnelly97a}
J.V.~Donnelly,  
\textsl{Post-Processing WIMS-AECL Results with Proc16},
Report FCC-RCP-001, Atomic Energy of Canada Limited, Chalk River, Ontario (1997).

\bibitem{Donnelly97c}
J.V.~Donnelly,  
\textsl{Wrfsp: Post-Processing Data from WIMS-AECL to RFSP},
Report FCC-RCP-006, Atomic Energy of Canada Limited, Chalk River, Ontario (1997).

\bibitem{freesteam}
See the home page at \url{http://freesteam.sourceforge.net/}.

\bibitem{optex1}
D. Rozon, A. H\'ebert and D. McNabb, ``The application of generalized perturbation theory and mathematical programming
to equilibrium refueling studies of a CANDU reactor," {\sl Nucl.Sci. Eng.}, {\bf 78}, 211 (1981).

\bibitem{optex2}
R. Chambon, E. Varin and D. Rozon, ``CANDU fuel management optimization using alternative gradient
methods," {\sl Ann. Nucl. Energy}, {\bf 34}, 1002 (2007).

\bibitem{optex3}
A. H\'ebert and H. Leroyer, ``A Presentation of the OPTEX Reflector Model," {\sl Nucl. Sci. Eng.},  {\bf 176}, 312--324 (2014).

\bibitem{recipie}
W.~H.~Press, B.~P.~Flannery, S.~A.~Teukolsky and W.~T.~Vetterling, {\sl Numerical Recipes in FORTRAN, Second Edition}, Cambridge University Press, Cambridge (1992).

\bibitem{armijo}
L. Armijo, ``Minimization of functions having Lipschitz continuous
first partial derivatives," {\sl Pacific journal of mathematics}, Vol. 16,
{\bf 1}, 1--3, 1966.

\bibitem{nocedal}
J. Nocedal, ``Updating Quasi-Newton Matrices With Limited Storage," {\sl Math. of Computation}, Vol. 35, {\bf 151}, 773--782 (1980).

\bibitem{sph1981}
A. H\'ebert, ``D\'eveloppement de la m\'ethode SPH: Homog\'en\'eisation de cellules dans un r\'eseau non uniforme et calcul des param\`etres de r\'eflecteur," Ph. D. thesis, CEA-N-2209 (1981).

\bibitem{sph2019}
A. H\'ebert, ``A general presentation of the SPH equivalence technique in non-fundamental mode cases," Submitted to {\sl Annals of Nucl. Energy} (2019).

\bibitem{inl}
V. Labour\'e, Y. Wang, J. Ortensi, S. Schunert, F. Gleicher, M. DeHart and R. Martineau, ``Hybrid super homogenization and discontinuity factor method for continuous finite element diffusion," {\sl Ann. nucl. Energy}, {\bf 128}, 443--454 (2019).

\bibitem{mixte-dual}
A. H\'ebert, ``Application of a Dual Variational Formulation to Finite Element Reactor Calculations'', {\sl Ann. nucl. Energy}, {\bf 20}, 823 - 845 (1993).

\bibitem{ane10a}
A. H\'ebert, ``Mixed-dual implementations of the of the simplified $P_n$ method," {\sl Ann. nucl. Energy}, {\bf 37}, 498--511 (2010).

\bibitem{ferland}
J. A. Ferland, ``A linear programming problem with an additional
quadratic constraint solved by parametric linear complementarity,"
Publication number 497, D\'epartement d'informatique et de recherche
op\'erationnelle, Universit\'e de Montr\'eal, January 1984.

\bibitem{fehri} M. F. Fehri, ``D\'eveloppement d'un code de thermohydraulique pour le couplage neutro\-nique/thermohydraulique,"
M. Sc. A. Thesis, \'Ecole Polytechnique de Montr\'eal (2008).

\bibitem{gallet} P. Gallet, ``D\'eveloppement d'un module de thermohydraulique simplifi\'ee dans le code DONJON4 pour l'\'etude multiphysique
des r\'eacteurs \`a eau pressuris\'ee," Ph. D. Thesis, \'Ecole Polytechnique de Montr\'eal (2014).

\bibitem{bowring}
R. W. Bowring, "Physical Model, Based on Bubble Detachment, and Calculation of Steam Voidage in the Subcooled
Region of a Heated Channel," OECD Report HPR-10, 1962.

\bibitem{saha-zuber}
P. Saha and N. Zuber, ``Point Of Net Vapor Generation and Vapor Void Fraction in Subcooled Boiling," {\sl Int. heat transfer conference}, Tokyo, Japan, 3 Sep 1974.

\bibitem{lahey}
R. T. Lahey and F. J. Moody, {\sl The Thermal-Hydraulics of a Boiling Water Nuclear Reactor},
American Nuclear Society Publications, U.S.A. (1977).

\bibitem{Chambon2014}
R. Chambon, ``Specifications and User Guide for {\tt NAP:} module in DRAGON/DONJON VERSION5
(Pin Power Reconstruction module)," Report IGE-345,
\'Ecole Polytechnique de Montr\'eal,
 Institut de G\'enie Nucl\'eaire (2014).

\bibitem{Fliscounakis2011}
M. Fliscounakis, E. Girardi and T. Courau, ``A Generalized Pin-Power Reconstruction Method for
Arbitrary Heterogeneous Geometries," M\&C 2011, Rio de Janero, Brasil, May 8--12 2011.

\bibitem{Rowlands}
G. Rowlands, ``Resonance Absorption and Non-Uniform Temperature Distributions," Journal of
Nuclear Energy Parts A/B, 16, pp 235-236 (1962).

\bibitem{PARCS}
T. Downar, Y. Xu and V. Seker, ``PARCS v3.0, U.S. NRC Core Neutronics Simulator, User Manual," Department of Nuclear Engineering and Radiological Science, University of Michigan, Ann Arbor, MI (2012).

\bibitem{GENPMAXS}
A. Ward, Y. Xu and T. Downar, ``GenPMAXS--v6.1.1, Code for Generating the PARCS Cross Section Interface File PMAXS," University of Michigan, 2013.

\end{thebibliography}
