\subsection{The \moc{PKINS:} module}\label{sect:pkins}

\vskip 0.2cm
The feedback parameters are responsible for the introduction of reactivity in the solution of the point-kinetics equations.
Some feedback parameters have their time variation set by {\sl time laws} defined in module  \moc{PKINI:} (See Sect.~\ref{sect:pkini}).
Some other are assumed constant during a {\sl time stage}, corresponding to a single call to module \moc{PKINS:}. The \moc{PKINS:}
module is used to solve the point-kinetics equations over a single time stage.

\vskip 0.08cm

\noindent
The \moc{PKINS:} module specification is:

\begin{DataStructure}{Structure \moc{PKINS:}}
$[$ \dusa{MAPFL} \moc{:=} $]$ \moc{PKINS:} \dusa{MAPFL} \moc{::} \dstr{descpkins}
\end{DataStructure}

\noindent where

\begin{ListeDeDescription}{mmmmmmmm}

\item[\dusa{MAPFL}] \texttt{character*12} name of the \dds{map} 
object containing fuel regions description and global parameter informations. This object is declared
in read-only mode if and only if keyword \moc{PICKR} is set.

\item[\dstr{descpkins}] structure describing the input data to the \moc{PKINS:} module. 

\end{ListeDeDescription}

\vskip 0.2cm

\subsubsection{Input data to the \moc{PKINS:} module}\label{sect:pkinsstr}

\begin{DataStructure}{Structure \dstr{descpkins}}
$[$ \moc{EDIT} \dusa{iprint} $]$ \\
\moc{TIME} \dusa{t0} \dusa{dt} \\
$\{~[$ \moc{POWER} \dusa{power} $|$ \moc{Y-INIT} (\dusa{y}(i),i=1,\dusa{ngroup+1}) $\}~]$ \\
$[~\{$ \moc{PICK}  {\tt >>} \dusa{power\_out} {\tt <<} $|$ \moc{PICKR}  {\tt >>} \dusa{rho} {\tt <<} $\}~]$ \\
;
\end{DataStructure}

\noindent where
\begin{ListeDeDescription}{mmmmmmmm}

\item[\moc{EDIT}] keyword used to set \dusa{iprint}.

\item[\dusa{iprint}] integer index used to control the printing on screen:
= 0 for no print; = 1 for minimum printing; larger values produce
increasing amounts of output.

\item[\moc{TIME}] keyword used to set the beginning-of-stage and duration times.

\item[\dusa{t0}] beginning-of-stage time (s).

\item[\dusa{dt}] stage duration (s). \dusa{dt} $=0.0$ if keyword \moc{PICKR} is set.

\item[\moc{POWER}] keyword used to set the beginning-of-stage reactor power.

\item[\dusa{power}] beginning-of-stage reactor power in MW.

\item[\moc{Y-INIT}] keyword used to set the beginning-of-stage solution of the point kinetics equations.

\item[\dusa{y}] beginning-of-stage value of a component of the beginning-of-stage solution. \dusa{ngroup} is the
number of delayed precursor groups.

\item[\moc{PICK}]  keyword used to recover the end-of-stage power (in MW) in a CLE-2000 variable.

\item[\dusa{power\_out}] \texttt{character*12} CLE-2000 variable name in which the extracted power value will be placed.

\item[\moc{PICKR}]  keyword used to recover the reactivity at time \dusa{t0} in a CLE-2000 variable.

\item[\dusa{rho}] \texttt{character*12} CLE-2000 variable name in which the reactivity value will be placed.

\end{ListeDeDescription}
\clearpage
