\subsection{The \moc{MOVDEV:} module}\label{sect:movdev}

\vskip 0.2cm
The \moc{MOVDEV:} module can be used for the transient simulations and
reactor control studies, which are related to the time-dependent rod-devices
displacement in the reactor core. The rods can be inserted into or extracted
from the reactor core, at constant or at variable speed of movement. The rod
positions are recomputed at every given time step of movement. The new rod
positions can be computed in several ways, based on either: current time increment
and movement speed; relative change in rod positions; \dusa{or} current rod
insertion level. The \moc{MOVDEV:} module allows the rod-devices to be
displaced individually or simultaneously in groups.\\

\noindent
The \moc{MOVDEV:} module specification is:

\begin{DataStructure}{Structure \moc{MOVDEV:}}
\dusa{DEVICE} \moc{:=} \moc{MOVDEV:}
\dusa{DEVICE} \moc{::} \dstr{descmove}
\end{DataStructure}

\noindent where

\begin{ListeDeDescription}{mmmmmmmm}

\item[\dusa{DEVICE}] \texttt{character*12} name of the \dds{device}
object that will be modified by the module. The rods positions are updated
according to the current time step of movement.

\item[\dstr{descmove}] structure describing the input data to the
\moc{MOVDEV:} module.

\end{ListeDeDescription}

\vskip 0.2cm

\subsubsection{Input data to the \moc{MOVDEV:} module}\label{sect:movdevstr}

It is possible to move several individual rods and/or several groups of rods
simultaneously. A user must be aware that a particular device will not be displaced
more than once during the same time step. Note that the input order of data to the
module must be respected. 

\begin{DataStructure}{Structure \dstr{descmove}}
$[$ \moc{EDIT} \dusa{iprint} $]$\\
\moc{DELT} \dusa{delt} \\
$[[$ $\{$ \moc{ROD} \dusa{id} $|$
\moc{GROUP} \dusa{igrp} $\}$ \\
$\{$ \moc{INSR} $|$ \moc{EXTR} $\}$ \\
$\{$ \moc{LEVEL} \dusa{value} $|$
\moc{DELH} \dusa{delh} $|$
\moc{SPEED} \dusa{speed} $\}$ $]]$  \\
;
\end{DataStructure}

\noindent where
\begin{ListeDeDescription}{mmmmmmmm}

\item[\moc{EDIT}] keyword used to set \dusa{iprint}.

\item[\dusa{iprint}] integer index used to control the printing on
screen: = 0 for no print; = 1 for minimum printing (default value);
larger values produce increasing amounts of output.

\item[\moc{DELT}] keyword used to set \dusa{delt}.

\item[\dusa{delt}] real value of the time increment for the current
time step, given in sec.

\item[\moc{ROD}] keyword used to specify the rod \dusa{id} number.

\item[\dusa{id}] integer identification number of a rod-type device to be
displaced. Each rod has a unique \dusa{id} number, ranging from 1 to
\dusa{nrod}, as been defined in the \moc{DEVINI:} module (see \Sect{devrodstr}).

\item[\moc{GROUP}] keyword used to specify a rod-group \dusa{igrp} number.

\item[\dusa{igrp}] integer number of a group of rods that will be displaced
simultaneously, with the same parameters of movement. Each group of
rod-devices has a unique \dusa{igrp} number, ranging from 1 to \dusa{ngrp},
as been defined in the \moc{DEVINI:} module (see \Sect{rodgroupstr}).

\item[\moc{INSR}] keyword used to specify that a particular rod or a
group of rods will be inserted into the reactor core during the period
of time \dusa{delt}.

\item[\moc{EXTR}] keyword used to specify that a particular rod or a
group of rods will be extracted from the reactor core during the period
of time \dusa{delt}.

\item[\moc{LEVEL}] keyword used to specify the new level \dusa{value}.

\item[\dusa{value}] real positive value of the rod insertion level at current
time step. This value will be used to compute the new rod position in the
reactor core. The insertion level is minimal (\dusa{value} = 0.0) when the
rod is completely withdrawn, and it is maximal (\dusa{value} = 1.0) when
the rod is fully inserted. For the partially inserted rod the insertion level
must be: 0.0 $<$ \dusa{value} $<$ 1.0

\item[\moc{DELH}] keyword used to specify the value \dusa{delh}.

\item[\dusa{delh}] real positive (absolute) value of the relative change in the
rod position during the period of time \dusa{delt}. This is a time-dependent
rod displacement along the rod movement axis, which must be given in cm.

\item[\moc{SPEED}] keyword used to set the current value of \dusa{speed}.

\item[\dusa{speed}] real positive (absolute) value of the rod movement
speed, given in cm/s. The rod speed can be kept constant or it can be
modified at any time step \dusa{delt}. The devices could also have the
different speeds of movement.

\end{ListeDeDescription}
\clearpage
