\subsection{Contents of \dir{device} data structure}\label{sect:device}

\vskip 0.2cm
A \dir{device} data structure is used to store several information related
to the reactor devices. This object has a signature {\tt L\_DEVICE};
it is created using the \moc{DEVINI:} module. The information contained in
this data structure can be used and updated in other DONJON modules
which are related to the devices, namely: \moc{LZC:}, \moc{DSET:},
\moc{MOVDEV:} and \moc{NEWMAC:} modules.

\subsubsection{The state-vector content}\label{sect:devicestate}
\noindent
The dimensioning parameters $\mathcal{S}_i$, which are stored in the state
vector for this data structure, represent:

\begin{itemize}

\item The type of reactor geometry $I_g = \mathcal{S}_1$
(only $I_g=7$ for \dusa{3D}-Cartesian geometry allowed)

\item The total number of rod-type devices $N_{rod} = \mathcal{S}_2$

\item The total number of the rod-type groups $N_{rgrp} = \mathcal{S}_3$

\item The total number of lzc-type devices $N_{lzc} = \mathcal{S}_4$

\item The total number of the lzc-type groups $N_{lgrp} = \mathcal{S}_5$

\item Type of control rod movement $I_{mov} = \mathcal{S}_6$ where
\begin{displaymath}
I_{\rm mov} = \left\{
\begin{array}{rl}
 1 & \textrm{Fading. A fraction of the fully inserted rod vanishes} \\
 2 & \textrm{Moving. The complete rod is moving (DONJON3-type movement).}
\end{array} \right.
\end{displaymath}

\end{itemize}

\subsubsection{The main \dir{device} directory}\label{sect:devicedir}
\noindent
The following records and sub-directories will be found on the first level
of \dir{device} directory:

\begin{DescriptionEnregistrement}{Records and sub-directories in \dir{device}
data structure}{7cm} 

\CharEnr
{SIGNATURE\blank{3}}{$*12$}
{Signature of the \dir{device} data structure ($\mathsf{SIGNA}=${\tt L\_DEVICE\blank{4}}).}

\IntEnr
{STATE-VECTOR}{$40$}
{Vector describing the various parameters associated with this data structure $\mathcal{S}_i$}

\DirlEnr
{DEV\_ROD\blank{5}}{$N_{rod}$}
{Sub-directories for each controller rod. A sub-directory is created for each
 controller rod according to the rod identification number.}

\DirlEnr
{ROD\_GROUP\blank{3}}{$N_{rgrp}$}
{Sub-directories for each group of rod-type devices. A sub-directory is created for
 each group of rod-type devices according to the rod-group identification number.}

\DirlEnr
{DEV\_LZC\blank{5}}{$N_{lzc}$}
{Sub-directories for each liquid zone controller. A sub-directory is created for
 each liquid controller according to the liquid controller identification number.}

\DirlEnr
{LZC\_GROUP\blank{3}}{$N_{lgrp}$}
{Sub-directories for each group of lzc-type devices. A sub-directory is created for
 each group of lzc-type devices according to the lzc-group identification number.}

\end{DescriptionEnregistrement}

\subsubsection{The \moc{DEV-ROD} sub-directories}\label{sect:devicerod}

\noindent
Inside each \moc{DEV-ROD} sub-directory, the following records will be found:

\begin{DescriptionEnregistrement}{Records in \moc{DEV-ROD} sub-directories}
{7.0cm} \label{tabl:tabrod}

\IntEnr
{ROD-ID\blank{6}}{$1$}
{The identification number of the rod.}

\CharEnr
{ROD-NAME\blank{4}}{$*12$}
{The identification name of the rod.}

\IntEnr
{ROD-PARTS\blank{3}}{$1$}
{The number of parts in the rod ($N_{\rm part}\ge 1$).}

\IntEnr
{AXIS\blank{8}}{$1$}
{The number used to identify the rod mouvement direction:
 = 1 along x-axis; = 2 along y-axis; =3 along z-axis.}

\IntEnr
{FROM\blank{8}}{$1$}
{The number used to identify the side of geometry, from which
 the controller rod is inserted into the reactor core along its direction
 of mouvement: = 1 if a rod is inserted from the highest position
 (e.g. from the top); = -1 if a rod is inserted from the lowest
 position (e.g. from the bottom).}

\RealEnr
{LENGTH\blank{6}}{$2$}{cm}
{The initial and final position coordinates of the full-inserted rod along its direction of movement. The
rod length is the distance between these two coordinates.}

\RealEnr
{CORE-LIMITS\blank{1}}{$6$}{cm}
{The initial and final position coordinates of the full core along each Cartesian direction.}

\RealEnr
{MAX-POS\blank{5}}{$6\times N_{\rm part}$}{cm}
{The limiting \dusa{3D}-Cartesian coordinates of the full-inserted rod. This
 data is given for each part of the rod.}

\IntEnr
{ROD-MIX\blank{5}}{$2\times N_{\rm part}$}
{The rod-type mixture indices. The first number corresponds to the
 inserted rod position and the second to the withdrawn rod position. This
 data is given for each part of the rod.}

\OptRealEnr
{LEVEL\blank{7}}{$1$}{*}{}
{The actual insertion level of the controller rod. This value must be
 between 0.0 for the full-withdrawn rod and 1.0 for the full-inserted rod.}

\OptRealEnr
{SPEED\blank{7}}{$1$}{*}{cm~s$^{-1}$}
{The speed of rod movement (insertion or extraction).}

\OptRealEnr
{TIME\blank{8}}{$1$}{*}{s}
{The time for the full rod insertion or extraction.}

\OptRealEnr
{ROD-POS\blank{5}}{$6\times N_{\rm part}$}{*}{cm}
{The actual \dusa{3D}-Cartesian coordinates of the rod. This
 data is given for each part of the rod.}

\end{DescriptionEnregistrement}

\subsubsection{The \moc{ROD-GROUP} sub-directories}\label{sect:rodgroup}

\noindent
Inside each \moc{ROD-GROUP} sub-directory, the following records will be found:

\begin{DescriptionEnregistrement}{Records in \moc{ROD-GROUP} sub-directories}
{7.0cm} \label{tabl:tabrodgroup}
 
\IntEnr
{GROUP-ID\blank{4}}{$1$}
{The identification number of the rod-group.}

\IntEnr
{NUM-ROD\blank{5}}{$1$}
{The total number $N_{rd}$ of rod-devices in the group.}

\IntEnr
{ROD-ID\blank{6}}{$N_{rd}$}
{An array of identification numbers of rods which belong to the same group.}

\end{DescriptionEnregistrement}

\subsubsection{The \moc{DEV-LZC} sub-directories}\label{sect:devicelzc}

\noindent
Inside each \moc{DEV-LZC} sub-directory, the following records will be found:

\begin{DescriptionEnregistrement}{Records in \moc{DEV-LZC} sub-directories}
{7.0cm} \label{tabl:tablzc}

\IntEnr
{LZC-ID\blank{6}}{$1$}
{The identification number of the liquid zone controller.}

\RealEnr
{MAX-POS\blank{5}}{$6$}{cm}
{The limiting \dusa{3D}-Cartesian coordinates of the whole liquid
 controller, including its empty and full parts.}

\IntEnr
{AXIS\blank{8}}{$1$}
{The number used to identify the water filling direction:
 = 1 along x-axis; = 2 along y-axis; =3 along z-axis.}

\RealEnr
{HEIGHT\blank{6}}{$1$}{cm}
{The water height of the full-filled controller along its direction of filling.}

\RealEnr
{LEVEL\blank{7}}{$1$}{}
{The actual water level of the liquid controller device. This value must
 be between 0.0 for the empty state and 1.0 for the full-filled state.}

\RealEnr
{EMPTY-POS\blank{3}}{$6$}{cm}
{The actual \dusa{3D}-Cartesian coordinates of the empty-part
 of liquid contoller.}

\RealEnr
{FULL-POS\blank{4}}{$6$}{cm}
{The actual \dusa{3D}-Cartesian coordinates of the full-part
 of liquid contoller.}

\IntEnr
{EMPTY-MIX\blank{3}}{$2$}
{The empty-part mixture number and the reference mixture number.}

\IntEnr
{FULL-MIX\blank{4}}{$2$}
{The full-part mixture number and the reference mixture number.}

\RealEnr
{RATE\blank{8}}{$1$}{$m^3 s^{-1}$}
{The water filling rate.}

\RealEnr
{TIME\blank{8}}{$1$}{s}
{The water filling time.}

\end{DescriptionEnregistrement}

\subsubsection{The \moc{LZC-GROUP} sub-directories}\label{sect:lzcgroup}

\noindent
Inside each \moc{LZC-GROUP} sub-directory, the following records will be found:

\begin{DescriptionEnregistrement}{Records in \moc{LZC-GROUP} sub-directories}
{7.0cm} \label{tabl:tablzcgroup}
 
\IntEnr
{GROUP-ID\blank{4}}{$1$}
{The identification number of the lzc-group.}

\IntEnr
{NUM-LZC\blank{5}}{$1$}
{The total number $N_{ld}$ of lzc-devices in the group.}

\IntEnr
{LZC-ID\blank{6}}{$N_{ld}$}
{An array of identification numbers of liquid controllers which belong to the same group.}

\end{DescriptionEnregistrement}
