\subsection{The \moc{XENON:} module}\label{sect:xenon}

\vskip 0.2cm
The \moc{XENON:} module is used to correct the Xenon distribution coming from an interpolation calculation.
 This module computes the new densities according to the bundle flux, and the equation providing the balance concentration of Xenon-135  :

\begin{eqnarray} \label{eqn:xe135eq}
N_{X_{eq}}=\frac{(Y_I+Y_X) \Sigma_f \phi}{\lambda_X + \sigma_X \phi}
\end{eqnarray}

\noindent where
\begin{itemize} 
\item $Y_I$ is the fission yield of I135
\item $Y_X$ is the fission yield of Xe135
\item $\sigma_X$ is the capture cross section of Xe135
\item $\lambda_X$ is the decay constant of Xe135
\item $\Sigma_f$ is the total fission cross section
\item $\phi$ is the bundle flux
\end{itemize}

\noindent
The \moc{XENON:} module specification is:

\begin{DataStructure}{Structure \moc{XENON:}}
 \dusa{MICROLIB} \moc{:=} \moc{XENON:} \dusa{MICROLIB}
$[$ \dusa{POWER} $]$  \\
\moc{::} \dstr{descxenon}
\end{DataStructure}

\noindent where

\begin{ListeDeDescription}{mmmmmmmm}

\item[\dusa{MICROLIB}] \texttt{character*12} name of a \dds{library} object,
that will be updated by the \moc{XENON:} module. The Xenon should be extracted in this library for the use of this module.

\item[\dusa{POWER}] \texttt{character*12} name of a \dds{power} object
containing the bundle fluxes, previously computed by the
\moc{FLPOW:} module. The fluxes should be normalized to the reactor power.

\item[\dstr{descxenon}] structure describing the input data to the \moc{XENON:} module.

\end{ListeDeDescription}

\vskip 0.2cm
\subsubsection{Input data to the \moc{XENON:} module}\label{sect:strxenon}

\noindent
Note that the input order must be respected.

\begin{DataStructure}{Structure \dstr{descxenon}}
$[$ \moc{EDIT} \dusa{iprint} $]$ \\
$[$ \moc{INIT} $]$ \\
;
\end{DataStructure}

\noindent where
\begin{ListeDeDescription}{mmmmmmmm}

\item[\moc{EDIT}] keyword used to set \dusa{iprint}.

\item[\dusa{iprint}] integer index used to control the printing on screen.

\item[\moc{INIT}] keyword used to indicate the initialization of the library for a recursive calculation using the \moc{XENON:} module. The Xenon concentration is set to zero for all the bundles.

\end{ListeDeDescription}
\clearpage
