\subsection{Contents of \dir{matex} data structure}\label{sect:matex}

\vskip 0.2cm
A \dir{matex} data structure is used to store several information related
to the reactor extended material index and geometry. This object has a
signature {\tt L\_MATEX}; it is created using the \moc{USPLIT:} module.
The information contained in this data structure can be used and updated
in other DONJON modules.

\subsubsection{The state-vector content}\label{sect:matexstate}

\noindent
The dimensioning parameters $\mathcal{S}_i$, which are stored in the state
vector for this data structure, represent:

\begin{itemize}

\item The number of energy groups $N_{gr} = \mathcal{S}_1$

\item The maximum number of material mixtures $N_m = \mathcal{S}_2$
($N_m$ equals to the total \\
number of material regions plus the number of device mixtures)

\item The number of reflector types $N_r = \mathcal{S}_3$

\item The number of fuel types $N_f = \mathcal{S}_4$

\item The total number of mixtures indices $N_{tot} = \mathcal{S}_5$
($N_{tot}$ equals to the total \\
number of mesh-splitted volumes plus the number of device mixtures)

\item The type of reactor geometry $I_g = \mathcal{S}_6$
(only $I_g=7$ for \dusa{3D}-Cartesian geometry or $I_g=9$ for
\dusa{3D}-Hexagonal geometry are allowed)

\item The total number of mesh-splitted volumes $N_{el} = \mathcal{S}_7$

\item The number of mesh-splitted volumes along x-axis $L_x = \mathcal{S}_8$

\item The number of mesh-splitted volumes along y-axis $L_y = \mathcal{S}_9$

\item The number of mesh-splitted volumes along z-axis $L_z = \mathcal{S}_{10}$

\end{itemize}

\subsubsection{The \dir{matex} directory}\label{sect:matexdir}

\noindent
The following records will be found on the \dir{matex} directory:

\begin{DescriptionEnregistrement}{Records in \dir{matex} data structure}{7cm} 

\CharEnr
 {SIGNATURE\blank{3}}{$*12$}
 {Signature of the \dir{matex} data structure ($\mathsf{SIGNA}=${\tt L\_MATEX\blank{5}}).}

\IntEnr
 {STATE-VECTOR}{$40$}
 {Vector describing the various parameters associated with this data structure $\mathcal{S}_i$}

\IntEnr
 {RMIX\blank{8}}{$N_r$}
 {The reflector-type mixture indices, as defined in the reactor geometry.}

\IntEnr
 {RTOT\blank{8}}{$N_r$}
 {The total number of reflector regions per each reflector type.}

\IntEnr
 {FMIX\blank{8}}{$N_f$}
 {The fuel-type mixture indices, as defined in the reactor geometry.}

\IntEnr
 {FTOT\blank{8}}{$N_f$}
 {The total number of fuel regions per each fuel type.}

\IntEnr
 {MAT\blank{9}}{$N_{tot}$}
 {The material mixture indices per each region and including the device
  mixtures. The fuel-type indices are set negative; the device indices are
  appended at the end of vector; the virtual-region indices are set to 0.}

\IntEnr
 {INDEX\blank{7}}{$N_{el}$}
 {The renumbered mixture indices. A unique number is associated
  with each mesh-splitted volume. The device indices are not included;
  the virtual-region indices are set to 0.}

\RealEnr
 {MESHX\blank{7}}{$L_x+1$}{}
 {The mesh-splitted coordinates along x-axis of the reactor geometry.}

\RealEnr
 {MESHY\blank{7}}{$L_y+1$}{}
 {The mesh-splitted coordinates along y-axis of the reactor geometry.}

\RealEnr
 {MESHZ\blank{7}}{$L_z+1$}{}
 {The mesh-splitted coordinates along z-axis of the reactor geometry.}

\RealEnr
 {H-FACTOR\blank{4}}{$N_m, N_{gr}$}{}
 {The h-factors per each mixture and per each energy group,
  as recovered from the extended \dir{macrolib} data structure.}

\end{DescriptionEnregistrement}
\clearpage
