\section{Contents of a \dir{deposition} directory}\label{sect:depositiondir}

This directory accumulates energy and charge deposition information gathered from coupled solutions of the Boltzmann and/or Boltzmann
Fokker-Planck transport equations.

\subsection{State vector content for the \dir{deposition} data structure}\label{sect:depositionstate}

The dimensioning parameters for this data structure, stored in the state vector
$\mathcal{S}^{dep}_{i}$, represent:

\begin{itemize}

\item The number of material mixtures $N_{\rm mix}=\mathcal{S}^{dep}_{1}$

\item The number of particules contributing to deposition $N_{\rm part}=\mathcal{S}^{dep}_{2}$

\item Charge deposition index $I_{\rm c}=\mathcal{S}^{dep}_{3}$:
\begin{displaymath}
I_{\rm c} = \left\{
\begin{array}{ll}
0 & \textrm{no charge deposition information}\\
1 & \textrm{charge deposition information is present.}
\end{array} \right.
\end{displaymath}

\item The number of Boltzmann transport equation iterations $N_{\rm iter}=\mathcal{S}^{dep}_{4}$
\end{itemize}

\subsection{The main \dir{deposition} directory}\label{sect:depositiondirmain}

On its first level, the following records and sub-directories will be found in the \dir{deposition} directory:

\begin{DescriptionEnregistrement}{Main records and sub-directories in \dir{deposition}}{6.0cm}
\CharEnr
  {SIGNATURE\blank{3}}{$*12$}
  {Signature of the data structure ($\mathsf{SIGNA}=${\tt L\_DEPOSITION})}
\IntEnr
  {STATE-VECTOR}{$40$}
  {Vector describing the various parameters associated with this data structure $\mathcal{S}^{dep}_{i}$,
  as defined in \Sect{depositionstate}.}
\CharEnr
  {PARTICLE-NAM}{($N_{\rm part}$)$*1$}
  {Character name associated to each particle.}
\RealEnr
  {VOLUME\blank{6}}{$N_{\rm mix}$}{cm$^{3}$}
  {Volumes.}
\DbleEnr
  {FLUX-NORM\blank{3}}{$1$}{$1$}
  {Flux normalization factor.}
\DbleEnr
  {EDEPOS\blank{6}}{$N_{\rm mix},N_{\rm part}$}{MeV$\cdot$cm$^{-3}\cdot$s$^{-1}$}
  {Energy deposition.}
\OptDbleEnr
  {CDEPOS\blank{6}}{$N_{\rm mix},N_{\rm part}$}{$I_{\rm c} = 1$}{electron$\cdot$cm$^{-3}\cdot$s$^{-1}$}
  {Charge deposition.}
\DbleEnr
  {EDEPOS\_TOT\blank{2}}{$N_{\rm mix}$}{MeV$\cdot$cm$^{-3}\cdot$s$^{-1}$}
  {Volume integrated energy deposition.}
\OptDbleEnr
  {CDEPOS\_TOT\blank{2}}{$N_{\rm mix}$}{$I_{\rm c} = 1$}{electron$\cdot$cm$^{-3}\cdot$s$^{-1}$}
  {Volume integrated charge deposition.}
\end{DescriptionEnregistrement}

\eject
