\section{Contents of a \dir{source} directory}\label{sect:sourcedir}

This directory contains the source components of a fixed source problem. This data structure is also useful for
{\sl fixed source eigenvalue problems} as used in the generalized perturbation theory (GPT).

\subsection{State vector content for the \dir{source} data structure}\label{sect:sourcestate}

The dimensioning parameters for this data structure, stored in the state vector
$\mathcal{S}^{sou}_{i}$, represent:

\begin{itemize}

\item The number of energy groups $N_{G}=\mathcal{S}^{sou}_{1}$

\item The number of unknowns per energy group $N_{U}=\mathcal{S}^{sou}_{2}$

\item The number of direct fixed sources $N_{D}=\mathcal{S}^{sou}_{3}$

\item The number of adjoint fixed sources $N_{A}=\mathcal{S}^{sou}_{4}$

\end{itemize}

\subsection{The main \dir{source} directory}\label{sect:sourcedirmain}

On its first level, the following records and sub-directories will be found in the \dir{source} directory:

\begin{DescriptionEnregistrement}{Main records and sub-directories in \dir{source}}{8.0cm}
\CharEnr
  {SIGNATURE\blank{3}}{$*12$}
  {Signature of the data structure ($\mathsf{SIGNA}=${\tt L\_SOURCE\blank{4}})}
\IntEnr
  {STATE-VECTOR}{$40$}
  {Vector describing the various parameters associated with this data structure $\mathcal{S}^{sou}_{i}$,
  as defined in \Sect{sourcestate}.}
\CharEnr
  {LINK.FLUX\blank{3}}{$*12$}
  {Name of the unperturbed {\sc flux} orthogonal to the fixed sources.}
\CharEnr
  {LINK.SYSTEM\blank{1}}{$*12$}
  {Name of the unperturbed {\sc system} object.}
\CharEnr
  {LINK.TRACK\blank{2}}{$*12$}
  {Name of the tracking object used to construct the system matrices.}
\OptDirlEnr
  {DSOUR\blank{7}}{$\mathcal{S}^{sou}_{3}$}{$\mathcal{S}^{sou}_{3}\ge 1$}
  {List of direct fixed source sub-directories. Each component of this list is a multigroup list of
  dimension $\mathcal{S}^{sou}_{1}$. Each component of the multigroup list is a real array of dimension
  $\mathcal{S}^{sou}_{2}$ containing a direct fixed source array.}
\OptDirlEnr
  {ASOUR\blank{7}}{$\mathcal{S}^{sou}_{4}$}{$\mathcal{S}^{sou}_{4}\ge 1$}
  {List of adjoint fixed source sub-directories. Each component of this list is a multigroup list of
  dimension $\mathcal{S}^{sou}_{1}$. Each component of the multigroup list is a real array of dimension
  $\mathcal{S}^{sou}_{2}$ containing an adjoint fixed source array}
\end{DescriptionEnregistrement}

\eject
