\section{Contents of a \dir{tracking} directory}\label{sect:trackingdir}

This directory contains the information resulting from an analysis of a geometry using a specific
calculation operator of DRAGON. 

\subsection{State vector content for the \dir{tracking} data structure}\label{sect:trackingstate}

The dimensioning parameters for this data structure, which are stored in the state vector
$\mathcal{S}$, represent:

\begin{itemize}

\item The number of regions $N_{r}=\mathcal{S}^{t}_{1}$

\item The number of unknown $N_{u}=\mathcal{S}^{t}_{2}$

\item The leakage flag $I_{L}=\mathcal{S}^{t}_{3}$ 

\begin{displaymath}
I_{L} = \left\{
\begin{array}{rl}
 0 & \textrm{Leakage is present} \\
 1 & \textrm{Leakage is absent} 
\end{array} \right.
\end{displaymath}

\item The maximum number of mixture used $M_{m}=\mathcal{S}^{t}_{4}$

\item The number of outer surfaces $N_{s}=\mathcal{S}^{t}_{5}$

\item Flag related to the double-heterogeneity option $\mathcal{S}^{t}_{40}$ where
\begin{displaymath}
\mathcal{S}^{t}_{40} = \left\{
\begin{array}{rl}
 0 & \textrm{the double-heterogeneity option is not used} \\
 1 & \textrm{the double-heterogeneity option is used.} \\
\end{array} \right.
\end{displaymath}

\end{itemize}

\subsection{The main \dir{tracking} directory}\label{sect:trackingdirmain}

On its first level, the
following records and sub-directories will be found in the \dir{tracking} directory:

\begin{DescriptionEnregistrement}{Main records and sub-directories in \dir{tracking}}{8.0cm}
\CharEnr
  {SIGNATURE\blank{3}}{$*12$}
  {Signature of the data structure ($\mathsf{SIGNA}=${\tt L\_TRACK\blank{5}}).}
\IntEnr
  {STATE-VECTOR}{$40$}
  {Vector describing the various parameters associated with this data structure $\mathcal{S}^{t}_{i}$,
  as defined in \Sect{trackingstate}.}
\CharEnr
  {TRACK-TYPE\blank{2}}{$*12$}
  {Type of tracking considered ($\mathsf{CDOOR}$). Allowed values are:
  {\tt 'EXCELL'}, {\tt 'SYBIL'}, {\tt 'MCCG'}, {\tt 'SN'}, {\tt 'BIVAC'} and {\tt 'TRIVAC'}.}
\CharEnr
  {LINK.GEOM\blank{3}}{$*12$}
  {Name of the {\sc geometry} on which the tracking is based.}
\CharEnr
  {TITLE\blank{7}}{$*72$}
  {Identification title ($\mathsf{TITLE}$) }
\IntEnr
  {MATCOD\blank{6}}{$\mathcal{S}^{t}_{1}$}
  {Region material $M_{r}$}
\IntEnr
  {KEYFLX\blank{6}}{$\mathcal{S}^{t}_{1}$}
  {Location in unknown vector of averaged regional flux $I_{r}$}
\RealEnr
  {VOLUME\blank{6}}{$\mathcal{S}^{t}_{1}$}{cm$^{3}$}
  {Region volumes $V_{r}$}
\OptIntEnr
  {BC-REFL+TRAN}{$\mathcal{S}^{t}_{5}$}{$\mathcal{S}^{t}_{5}\ge 1$}
  {Reflection/transmission matrix localisation operator $T_{s}$}
\OptDirEnr
  {FUNC-TABLES\blank{1}}{*}
  {Directory containing Bickey or/and exponential function tables.} 
\OptDirEnr
  {BIHET\blank{7}}{$\mathcal{S}^{t}_{40}=1$}
  {Sub-directory containing the data related to a double heterogeneity geometry.
  The specification of this directory is given in \Sect{bihettrackingdir}} 
\end{DescriptionEnregistrement}

In addition to the above records, the main \dir{tracking} directory will also contain information
which is specific to each tracking module. This information will be described in the following
sub-sections. Also note that the contents of the $\mathcal{S}^{t}_{i}$ vector for $i\ge 6$ will depend
on the specific tracking module and will be defined in the next sub-sections.

\input{SectDsybil.tex}       % Description of a Sybil tracking
\input{SectDexcell.tex}      % Description of an Excell tracking
\input{SectDmccg.tex}        % Description of a MCCG tracking
\input{SectDsn.tex}          % Description of a SN tracking
\input{SectDbivac.tex}       % Description of a Bivac tracking
\input{SectDtrivac.tex}      % Description of a Trivac tracking
\input{SectDbihet.tex}       % Description of a Bihet tracking
