\subsection{The \moc{CFC:} module}\label{sect:CFCData}

The \moc{CFC:} module is used to generate a Feedback Model database required for a full core
calculation in DONJON.\cite{sissaoui} The general
specifications of this module are:

\begin{DataStructure}{Structure \dstr{CFC:}}
\dusa{CFCNAM} \moc{:=} \moc{CFC:} $[$ \dusa{CFCNAM} $]$ \\
\hspace*{1.0cm} (\dusa{CPONAM}($i$), $i$=1,28) \moc{::} \dstr{desccfc}
\end{DataStructure}

\noindent 
 where

\begin{ListeDeDescription}{mmmmmmmm} 

\item[\dusa{CFCNAM}] \verb|character*12| name of the \dds{fbmxsdb} data structure containing
the Feedback Model reactor database. The reactor database can be updated if \dusa{CFCNAM}
appears on the RHS.

\item[\dusa{CPONAM}] \verb|character*12| name of read only \dds{cpo} data structures. There
are 28 different \dds{cpo} data structures required here each containing respectively

\begin{enumerate}

\item the reactor reference cross section.

\item cell cross section for the first fuel temperature.

\item cell cross section for the second fuel temperature.

\item cell cross section for the first coolant temperature.

\item cell cross section for the second coolant temperature.

\item cell cross section for the first moderator temperature.

\item cell cross section for the second moderator temperature. 

\item cell cross section for the first coolant density. 

\item cell cross section for the second coolant density. 

\item cell cross section for the first moderator density.

\item cell cross section for the second moderator density.

\item cell cross section for a different concentration of boron. 

\item cell cross section for a different moderator purity. 

\item cell cross section for a different concentration of xenon. 

\item cell cross section for a different concentration of samarium.

\item cell cross section for a different concentration of neptunium.

\item cell cross section for the spectral mixed effect fuel/coolant density.

\item cell cross section for the spectral mixed effect coolant density/temperature.

\item cell cross section for low power history. 

\item cell cross section for intermediate power history. 

\item cell cross section for high power history. 

\item reactor reference moderator cross section.

\item moderator cross section for the first moderator temperature.

\item moderator cross section for the second moderator temperature.

\item moderator cross section for the first moderator density. 

\item moderator cross section for the second moderator density.

\item moderator cross section for a different concentration of boron. 

\item moderator cross section for a different moderator purity.

\end{enumerate}

\item[\dstr{desccfc}] structure containing the input data to this module (see
\Sect{desccfc}).

\end{ListeDeDescription}


\subsubsection{Data input for module \moc{CFC:}}\label{sect:desccfc}

\begin{DataStructure}{Structure \dstr{desccfc}}
$[$ \moc{EDIT} \dusa{iprint} $]$ \\
$[$ \moc{INFOR} \dusa{TITLE} $]$ \\
$[$ \moc{DNAME} \dusa{RNANE} $]$ \\
$[$ \moc{PWR} \dusa{powerref} \dusa{powerup} \dusa{powerint} \dusa{powerdown} $]$ \\
$[$ \moc{TCOOL} \dusa{tcoolref} \dusa{tcoolup} \dusa{tcooldown} $]$ \\
$[$ \moc{TMODE} \dusa{tmoderef} \dusa{tmodeup} \dusa{tmodedown} $]$ \\
$[$ \moc{TFUEL} \dusa{tfuelref} \dusa{tfuelup} \dusa{tfueldown} $]$ \\
$[$ \moc{RHOC} \dusa{denscool}$]$ \\
$[$ \moc{RHOM} \dusa{densmode}$]$ \\
$[$ \moc{XIR} \dusa{purityref} \dusa{puritydown} $]$ \\
\end{DataStructure}

\noindent where


\begin{ListeDeDescription}{mmmmmmmm} 

\item[\moc{EDIT}] keyword used to modify the print level \dusa{iprint}.

\item[\dusa{iprint}] index used to control the printing of the module. 

\item[\moc{INFOR}] keyword which allows to set the title.

\item[\dusa{TITLE}] \verb|character*72| title associated to the reactor database generated. 

\item[\moc{DNAME}] keyword to set a specific database name in the data
structure.
 
\item[\dusa{RNAME}] \verb|character*12| name of the feedback database. 

\item[\moc{PWR}] keyword to specify power used for evolution for power history.
 
\item[\dusa{powerref}]  power value for regular power history (\dusa{CPONAM} default). 

\item[\dusa{powerup}]  power value for high power history (\dusa{CPONAM} 21). 

\item[\dusa{powerint}]  power value for intermediate power history (\dusa{CPONAM} 20). 

\item[\dusa{powerdown}]  power value for low power history (\dusa{CPONAM} 19). 

\item[\moc{TCOOL}] keyword to specify coolant temperature used for regular evolution and perturbed cases.
 
\item[\dusa{tcoolref}]  normal coolant temperature (\dusa{CPONAM} default). 

\item[\dusa{tcoolup}]  high coolant temperature (\dusa{CPONAM} 4). 

\item[\dusa{tcooldown}]  low coolant temperature (\dusa{CPONAM} 5). 

\item[\moc{TMODE}] keyword to specify moderator temperature used for regular evolution and perturbed cases.
 
\item[\dusa{tmoderef}]  normal moderator temperature (\dusa{CPONAM} default). 

\item[\dusa{tmodeup}]  high moderator temperature (\dusa{CPONAM} 6 and 23). 

\item[\dusa{tmodedown}]  low moderator temperature (\dusa{CPONAM} 7 and 24). 

\item[\moc{TFUEL}] keyword to specify fuel temperature used for regular evolution and perturbed cases.
 
\item[\dusa{tfuelref}]  normal fuel temperature (\dusa{CPONAM} default). 

\item[\dusa{tfuelup}]  high fuel temperature (\dusa{CPONAM} 2). 

\item[\dusa{tfueldown}]  low fuel temperature (\dusa{CPONAM} 3). 

\item[\moc{RHOC}] keyword to specify coolant density used for regular evolution.
 
\item[\dusa{denscool}]  normal  coolant density (\dusa{CPONAM} default). 

\item[\moc{RHOM}] keyword to specify moderator density used for regular evolution.
 
\item[\dusa{densmode}]  normal moderator density (\dusa{CPONAM} default). 

\item[\moc{XIR}] keyword to specify water purity ($D_2O$ content) used for regular evolution and perturbed cases.
 
\item[\dusa{purityref}]  normal moderator purity (fraction of $D_2O$ in water) (\dusa{CPONAM} default). 

\item[\dusa{puritydown}]  perturbed moderator purity (fraction of $D_2O$ in water) (\dusa{CPONAM} 13 and 28). 

\end{ListeDeDescription}


Note: Other perturbed values are recovered directly from the concentrations and isotope densities stored in the different \dusa{CPONAM}. 
\clearpage
