\subsection{The DRAGON Data Structures}\label{sect:DragonDataStructures}

The transfer of information between the DRAGON execution modules is
ensured by well defined data structure. They are generally created or
modified directly by one of the modules of DRAGON or by one of the utility
modules. Here we will give a brief description of these data structures but a
more complete description of their content is also available upon
request.\cite{DragonDataStructures} These data structures are memory-resident or
persistent (i.e., XSM--type) objects.

\begin{ListeDeDescription}{mmmmmmmm}

\item[\dds{macrolib}]  a standard data structure used by DRAGON to transfer
group-ordered macroscopic cross sections between its modules. It can be a
stand-alone structure or it can be included into a larger structure, such as a
\dds{microlib} or an \dds{edition} structure. It can be created by the
\moc{MAC:}, \moc{LIB:} and \moc{EDI:} modules. It can also be modified
by the \moc{SHI:}, \moc{TONE:}, \moc{USS:} and \moc{EVO:} modules. Such a structure (either stand-alone
or as part of a \dds{microlib}) is also required for a successful execution of the
\moc{ASM:} and \moc{FLU:} modules.

\item[\dds{microlib}] a standard data structure used by DRAGON to transfer
microscopic and macroscopic cross sections between its modules. It always
include a \dds{macrolib} substructure. It can be a stand-alone structure or
included into a larger structure, such as an \dds{edition} structure. It
can be created by the \moc{LIB:} and \moc{EDI:} modules. It can also be
modified by the \moc{MAC:}, \moc{SHI:}, \moc{TONE:}, \moc{USS:} and \moc{EVO:} modules. 

\item[\dds{geometry}] a standard data structure used by DRAGON to transfer
the geometry between its modules. It can be a stand-alone structure or
included into a larger structure, such as another \dds{geometry} structure. It can be created by the \moc{GEO:} module. Such a structure is also
required directly for a successful execution of the tracking modules (\moc{SYBILT:},
\moc{EXCELT:} and \moc{MCCGT:}).

\item[\dds{tracking}] a standard data structure used by DRAGON to transfer
the general tracking information between its modules. It is a stand-alone
structure. It can be created by the \moc{SYBILT:}, \moc{EXCELT:} and \moc{MCCGT:}
modules. Such a structure is also required directly for a successful execution of
the \moc{ASM:} module.

\item[\dds{asmpij}] a standard data structure used by DRAGON to transfer the
multigroup response and collision probability matrices between its modules. It
is a stand-alone structure. It is created by the \moc{ASM:} module. Such a
structure is also required directly for a successful execution of the
\moc{FLU:} module.

\item[\dds{fluxunk}] a standard data structure used by DRAGON to transfer the
fluxes  between its modules. It is a stand-alone structure. It is created
by the \moc{FLU:} module. Such a structure is also
required for a successful execution of the \moc{EDI:} and \moc{EVO:} modules.

\item[\dds{edition}] a standard data structure used by DRAGON to store
condensed and merged microscopic and macroscopic cross sections. It is a
stand-alone structure but can contain \dds{macrolib} and \dds{microlib}
substructure. It is created by the \moc{EDI:} module. Such
a structure is also required for a successful execution of the \moc{COMPO:}
module.

\item[\dds{burnup}] a standard data structure used by DRAGON to store
burnup informations. It is created by the \moc{EVO:} module.  Such
a structure is also required for a successful execution of the \moc{COMPO:}
module.

\item[\dds{draglib}] a standard data structure used by DRAGON (input) to recover isotopic--, dilution--
and temperature--dependent information, including multigroup microscopic cross
sections and burnup data. This is a stand-alone structure that is generally
stored on a persistent LCM object. It may be created
by the {\tt dragr} module of {\tt NJOY}.

\item[\dds{cpo}] a standard data structure used by DRAGON to store
a simplified reactor dabase. It is a stand-alone structure that must be stored on a
linked list or an XSM file. It is created by the \moc{CPO:} module. It is required for a successful execution of the \moc{CFC:}
module. It can be used by the \moc{CRE:} module of DONJON.

\item[\dds{multicompo}] a standard data structure used by DRAGON (output) to store
reactor related information and to classified it using tuples of local and global
parameters. This is a stand-alone structure that is generally
stored on a persistent LCM object. It is created by the \moc{COMPO:} module.

\item[\dds{saphyb}] a standard data structure used by APOLLO2 and DRAGON (output) to store
reactor related information and to classified it using tuples of global
parameters. This is a stand-alone structure that is generally
stored on a persistent LCM object. It is created by the \moc{SAP:} module.

\item[\dds{fbmxsdb}] a standard data structure used by DRAGON to store
a full reactor cross section database with Feedback coefficients. 
It is a stand-alone structure that must be stored on a linked list or an XSM file. It is created by the \moc{CFC:} module. It can be used by the \moc{AFM:} module of DONJON.\cite{sissaoui}

\end{ListeDeDescription}

