\subsection{Main Updates in DRAGON}\label{sect:Updates}

The frozen version (DRAGON Release 3.06) has seen a large number of changes since
the first official release of the code (DRAGON\_960627).

\vskip 0.15cm

The following DRAGON package (DRAGON Version4) is an evolution of the frozen version,
released as an attempt to introduce innovative capabilities:

\begin{itemize}

\item The new self-shielding module \moc{USS:} allow increased accuracy and better representation
of phenomena such as {\sl distributed self-shielding effects} and {\sl mutual self-shielding effects}.

\item The new flux solution solver MCCG is an implementation of the long characteristics method proposed
by Igor Suslov. This solver is initiated by the new tracking module \moc{MCCGT:}.

\item The new flux solution module \moc{FLU:} is a complete rewrite of the outer iteration
for the multigroup flux calculation that is now compatible with the method of characteristics and with
any other approach requiring inner iterations. The \moc{MOCC:} module is no longer required.

\item The burnup module \moc{EVO:} was extended to take into account energy produced by radioactive
decay and by reactions other than fission.

\item The new module \moc{COMPO:} is used to create and increment a multiparameter reactor database. The
module The companion module \moc{NCR:} is used to interpolate an existing multiparameter reactor database.

\item The flux solution solver SYBIL related to 2D assembly calculations was extended to allow
sectorization of the cells.

\item The method of discrete ordinates is implemented in tracking module \moc{SNT:}.

\item The \moc{EXCELL:} module has been removed, but its capability is now implemented using the \moc{XCLL} keyword
in \moc{EXCELT:}.

\item The \moc{LIB:} module can access NDAS-formatted cross-section libraries.

\end{itemize}

\vskip 0.15cm

The current DRAGON package (DRAGON Version5) is a rewrite of the code around the GANLIB5 kernel\cite{ganlib5}, intended to be 64-bit clean.
